---
title: "Phenology Simulation"
author: "David S, Mason"
date: "6/28/2021"
output: pdf_document
---
In this first part, I use a Poisson distribution to generate seed arrival data for 3 months in different seasons. Then, I assign values for categorical predictors. Also, I randomly generate the fruit availability using a binomial distribution for whether or not a sampling point has fruit. Finally, I repeat this process for each species. I set the mean higher whenever the phenology of the species matches the timing of sampling.
```{r}
library(tidyverse)
x <- seq(1:50)

### ILGL ####

# JANUARY
# ILGL Winter burn 
ILGL.W.Jan <- as.data.frame(rpois(7, lambda = 20))
ILGL.W.Jan <- rename(ILGL.W.Jan, "SEEDS" = "rpois(7, lambda = 20)")
ILGL.W.Jan$SPECIES <- "ILGL"
ILGL.W.Jan$DATE <- "JAN"
ILGL.W.Jan$TREATMENT <- "W"
ILGL.W.Jan$PHENOLOGY <- "W"
ILGL.W.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
ILGL.W.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16")
ILGL.W.Jan$FA <- sum(rbinom(15,1, 0.2))/15

# ILGL other burns 
ILGL.SpSuF.Jan <- as.data.frame(rpois(21, lambda = 10))
ILGL.SpSuF.Jan <- rename(ILGL.SpSuF.Jan, "SEEDS" = "rpois(21, lambda = 10)")
ILGL.SpSuF.Jan$SPECIES <- "ILGL"
ILGL.SpSuF.Jan$DATE <- "JAN"
ILGL.SpSuF.Jan$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F")
ILGL.SpSuF.Jan$PHENOLOGY <- "W"
ILGL.SpSuF.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
ILGL.SpSuF.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16")
ILGL.SpSuF.Jan$FA <- sum(rbinom(15,1, 0.5))/15
ILGL.Jan <- rbind(ILGL.SpSuF.Jan, ILGL.W.Jan)

# JUNE 

# ILGL all burns 
ILGL.June <- as.data.frame(rpois(28, lambda = 5))
ILGL.June <- rename(ILGL.June, "SEEDS" = "rpois(28, lambda = 5)")
ILGL.June$SPECIES <- "ILGL"
ILGL.June$DATE <- "JUNE"
ILGL.June$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
ILGL.June$PHENOLOGY <- "W"
ILGL.June$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
ILGL.June$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
ILGL.June$FA <- sum(rbinom(15,1, 0.5))/15

# SEPT 

# ILGL all burns 
ILGL.Sept <- as.data.frame(rpois(28, lambda = 5))
ILGL.Sept <- rename(ILGL.Sept, "SEEDS" = "rpois(28, lambda = 5)")
ILGL.Sept$SPECIES <- "ILGL"
ILGL.Sept$DATE <- "SEPT"
ILGL.Sept$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
ILGL.Sept$PHENOLOGY <- "W"
ILGL.Sept$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
ILGL.Sept$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
ILGL.Sept$FA <- sum(rbinom(15,1, 0.5))/15

# COMBINE ILGL
ILGL <- rbind(ILGL.Jan,ILGL.June,ILGL.Sept)

### RUBUS ####
# JUNE
# RUBUS June burn 
RUBUS.SU.JUNE <- as.data.frame(rpois(7, lambda = 30))
RUBUS.SU.JUNE <- rename(RUBUS.SU.JUNE, "SEEDS" = "rpois(7, lambda = 30)")
RUBUS.SU.JUNE$SPECIES <- "RUBUS"
RUBUS.SU.JUNE$DATE <- "JUNE"
RUBUS.SU.JUNE$TREATMENT <- "SU"
RUBUS.SU.JUNE$PHENOLOGY <- "SU"
RUBUS.SU.JUNE$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
RUBUS.SU.JUNE$PLOT <- c("1", "2", "3", "13", "14", "15", "16")
RUBUS.SU.JUNE$FA <- sum(rbinom(15,1, 0.2))/15

# RUBUS other burns 
RUBUS.SpFW.JUNE <- as.data.frame(rpois(21, lambda = 15))
RUBUS.SpFW.JUNE <- rename(RUBUS.SpFW.JUNE, "SEEDS" = "rpois(21, lambda = 15)")
RUBUS.SpFW.JUNE$SPECIES <- "RUBUS"
RUBUS.SpFW.JUNE$DATE <- "JUNE"
RUBUS.SpFW.JUNE$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"W","W","W","W","W","W","W",
															"F","F","F","F","F","F","F")
RUBUS.SpFW.JUNE$PHENOLOGY <- "SU"
RUBUS.SpFW.JUNE$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
RUBUS.SpFW.JUNE$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16")
RUBUS.SpFW.JUNE$FA <- sum(rbinom(15,1, 0.7))/15
RUBUS.June <- rbind(RUBUS.SU.JUNE, RUBUS.SpFW.JUNE)

# January
# Rubus JAN all burns 
Rubus.Jan <- as.data.frame(rpois(28, lambda = 5))
Rubus.Jan <- rename(Rubus.Jan, "SEEDS" = "rpois(28, lambda = 5)")
Rubus.Jan$SPECIES <- "RUBUS"
Rubus.Jan$DATE <- "JAN"
Rubus.Jan$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
Rubus.Jan$PHENOLOGY <- "SU"
Rubus.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
Rubus.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
Rubus.Jan$FA <- sum(rbinom(15,1, 0.5))/15

# September
# Rubus Sept all burns 
Rubus.Sept <- as.data.frame(rpois(28, lambda = 10))
Rubus.Sept <- rename(Rubus.Sept, "SEEDS" = "rpois(28, lambda = 10)")
Rubus.Sept$SPECIES <- "RUBUS"
Rubus.Sept$DATE <- "SEPT"
Rubus.Sept$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
Rubus.Sept$PHENOLOGY <- "SU"
Rubus.Sept$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
Rubus.Sept$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
Rubus.Sept$FA <- sum(rbinom(15,1, 0.5))/15

RUBUS <- rbind(RUBUS.June, Rubus.Jan, Rubus.Sept)

### RHUS ####
# SEPT
# RHUS Sept burn 
RHUS.F.SEPT <- as.data.frame(rpois(7, lambda = 25))
RHUS.F.SEPT <- rename(RHUS.F.SEPT, "SEEDS" = "rpois(7, lambda = 25)")
RHUS.F.SEPT$SPECIES <- "RHUS"
RHUS.F.SEPT$DATE <- "SEPT"
RHUS.F.SEPT$TREATMENT <- "F"
RHUS.F.SEPT$PHENOLOGY <- "F"
RHUS.F.SEPT$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
RHUS.F.SEPT$PLOT <- c("1", "2", "3", "13", "14", "15", "16")
RHUS.F.SEPT$FA <- sum(rbinom(15,1, 0.24))/15

# RHUS Sept other burns 
RHUS.SpSuW.SEPT <- as.data.frame(rpois(21, lambda = 12))
RHUS.SpSuW.SEPT <- rename(RHUS.SpSuW.SEPT, "SEEDS" = "rpois(21, lambda = 12)")
RHUS.SpSuW.SEPT$SPECIES <- "RHUS"
RHUS.SpSuW.SEPT$DATE <- "SEPT"
RHUS.SpSuW.SEPT$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"W","W","W","W","W","W","W",
															"SU","SU","SU","SU","SU","SU","SU")
RHUS.SpSuW.SEPT$PHENOLOGY <- "F"
RHUS.SpSuW.SEPT$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
RHUS.SpSuW.SEPT$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16")
RHUS.SpSuW.SEPT$FA <- sum(rbinom(15,1, 0.5))/15
RHUS.Sept <- rbind(RHUS.F.SEPT, RHUS.SpSuW.SEPT)

# January
# RHUS all burns 
Rhus.Jan <- as.data.frame(rpois(28, lambda = 8))
Rhus.Jan <- rename(Rhus.Jan, "SEEDS" = "rpois(28, lambda = 8)")
Rhus.Jan$SPECIES <- "RHUS"
Rhus.Jan$DATE <- "JAN"
Rhus.Jan$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
Rhus.Jan$PHENOLOGY <- "F"
Rhus.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
Rhus.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
Rhus.Jan$FA <- sum(rbinom(15,1, 0.5))/15

# June
# RHUS all burns 
Rhus.June <- as.data.frame(rpois(28, lambda = 9))
Rhus.June <- rename(Rhus.June, "SEEDS" = "rpois(28, lambda = 9)")
Rhus.June$SPECIES <- "RHUS"
Rhus.June$DATE <- "JUNE"
Rhus.June$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
Rhus.June$PHENOLOGY <- "F"
Rhus.June$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
Rhus.June$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
Rhus.June$FA <- sum(rbinom(15,1, 0.5))/15

RHGL <- rbind(Rhus.June,Rhus.Jan, RHUS.Sept)





### SMRO ####

# JANUARY
# SMRO Winter burn 
SMRO.W.Jan <- as.data.frame(rpois(7, lambda = 22))
SMRO.W.Jan <- rename(SMRO.W.Jan, "SEEDS" = "rpois(7, lambda = 22)")
SMRO.W.Jan$SPECIES <- "SMRO"
SMRO.W.Jan$DATE <- "JAN"
SMRO.W.Jan$TREATMENT <- "W"
SMRO.W.Jan$PHENOLOGY <- "W"
SMRO.W.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
SMRO.W.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16")
SMRO.W.Jan$FA <- sum(rbinom(15,1, 0.2))/15

# SMRO other burns 
SMRO.SpSuF.Jan <- as.data.frame(rpois(21, lambda = 9))
SMRO.SpSuF.Jan <- rename(SMRO.SpSuF.Jan, "SEEDS" = "rpois(21, lambda = 9)")
SMRO.SpSuF.Jan$SPECIES <- "SMRO"
SMRO.SpSuF.Jan$DATE <- "JAN"
SMRO.SpSuF.Jan$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F")
SMRO.SpSuF.Jan$PHENOLOGY <- "W"
SMRO.SpSuF.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
SMRO.SpSuF.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16")
SMRO.SpSuF.Jan$FA <- sum(rbinom(15,1, 0.5))/15
SMRO.Jan <- rbind(SMRO.SpSuF.Jan, SMRO.W.Jan)

# JUNE 

# SMRO all burns 
SMRO.June <- as.data.frame(rpois(28, lambda = 6))
SMRO.June <- rename(SMRO.June, "SEEDS" = "rpois(28, lambda = 6)")
SMRO.June$SPECIES <- "SMRO"
SMRO.June$DATE <- "JUNE"
SMRO.June$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
SMRO.June$PHENOLOGY <- "W"
SMRO.June$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
SMRO.June$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
SMRO.June$FA <- sum(rbinom(15,1, 0.5))/15

# SEPT 

# SMRO all burns 
SMRO.Sept <- as.data.frame(rpois(28, lambda = 4))
SMRO.Sept <- rename(SMRO.Sept, "SEEDS" = "rpois(28, lambda = 4)")
SMRO.Sept$SPECIES <- "SMRO"
SMRO.Sept$DATE <- "SEPT"
SMRO.Sept$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
SMRO.Sept$PHENOLOGY <- "W"
SMRO.Sept$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
SMRO.Sept$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
SMRO.Sept$FA <- sum(rbinom(15,1, 0.5))/15

# COMBINE SMRO
SMRO <- rbind(SMRO.Jan,SMRO.June,SMRO.Sept)

### CAAM ####
# JUNE
# CAAM June burn 
CAAM.SU.JUNE <- as.data.frame(rpois(7, lambda = 40))
CAAM.SU.JUNE <- rename(CAAM.SU.JUNE, "SEEDS" = "rpois(7, lambda = 40)")
CAAM.SU.JUNE$SPECIES <- "CAAM"
CAAM.SU.JUNE$DATE <- "JUNE"
CAAM.SU.JUNE$TREATMENT <- "SU"
CAAM.SU.JUNE$PHENOLOGY <- "SU"
CAAM.SU.JUNE$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
CAAM.SU.JUNE$PLOT <- c("1", "2", "3", "13", "14", "15", "16")
CAAM.SU.JUNE$FA <- sum(rbinom(15,1, 0.2))/15

# CAAM other burns 
CAAM.SpFW.JUNE <- as.data.frame(rpois(21, lambda = 18))
CAAM.SpFW.JUNE <- rename(CAAM.SpFW.JUNE, "SEEDS" = "rpois(21, lambda = 18)")
CAAM.SpFW.JUNE$SPECIES <- "CAAM"
CAAM.SpFW.JUNE$DATE <- "JUNE"
CAAM.SpFW.JUNE$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"W","W","W","W","W","W","W",
															"F","F","F","F","F","F","F")
CAAM.SpFW.JUNE$PHENOLOGY <- "SU"
CAAM.SpFW.JUNE$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
CAAM.SpFW.JUNE$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16")
CAAM.SpFW.JUNE$FA <- sum(rbinom(15,1, 0.7))/15
CAAM.June <- rbind(CAAM.SU.JUNE, CAAM.SpFW.JUNE)

# January
# CAAM JAN all burns 
CAAM.Jan <- as.data.frame(rpois(28, lambda = 8))
CAAM.Jan <- rename(CAAM.Jan, "SEEDS" = "rpois(28, lambda = 8)")
CAAM.Jan$SPECIES <- "CAAM"
CAAM.Jan$DATE <- "JAN"
CAAM.Jan$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
CAAM.Jan$PHENOLOGY <- "SU"
CAAM.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
CAAM.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
CAAM.Jan$FA <- sum(rbinom(15,1, 0.5))/15

# September
# CAAM Sept all burns 
CAAM.Sept <- as.data.frame(rpois(28, lambda = 15))
CAAM.Sept <- rename(CAAM.Sept, "SEEDS" = "rpois(28, lambda = 15)")
CAAM.Sept$SPECIES <- "CAAM"
CAAM.Sept$DATE <- "SEPT"
CAAM.Sept$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
CAAM.Sept$PHENOLOGY <- "SU"
CAAM.Sept$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
CAAM.Sept$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
CAAM.Sept$FA <- sum(rbinom(15,1, 0.5))/15

CAAM <- rbind(CAAM.June, CAAM.Jan, CAAM.Sept)

### PHAM ####
# SEPT
# PHAM Sept burn 
PHAM.F.SEPT <- as.data.frame(rpois(7, lambda = 32))
PHAM.F.SEPT <- rename(PHAM.F.SEPT, "SEEDS" = "rpois(7, lambda = 32)")
PHAM.F.SEPT$SPECIES <- "PHAM"
PHAM.F.SEPT$DATE <- "SEPT"
PHAM.F.SEPT$TREATMENT <- "F"
PHAM.F.SEPT$PHENOLOGY <- "F"
PHAM.F.SEPT$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
PHAM.F.SEPT$PLOT <- c("1", "2", "3", "13", "14", "15", "16")
PHAM.F.SEPT$FA <- sum(rbinom(15,1, 0.24))/15

# PHAM Sept other burns 
PHAM.SpSuW.SEPT <- as.data.frame(rpois(21, lambda = 17))
PHAM.SpSuW.SEPT <- rename(PHAM.SpSuW.SEPT, "SEEDS" = "rpois(21, lambda = 17)")
PHAM.SpSuW.SEPT$SPECIES <- "PHAM"
PHAM.SpSuW.SEPT$DATE <- "SEPT"
PHAM.SpSuW.SEPT$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"W","W","W","W","W","W","W",
															"SU","SU","SU","SU","SU","SU","SU")
PHAM.SpSuW.SEPT$PHENOLOGY <- "F"
PHAM.SpSuW.SEPT$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
PHAM.SpSuW.SEPT$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16")
PHAM.SpSuW.SEPT$FA <- sum(rbinom(15,1, 0.5))/15
PHAM.Sept <- rbind(PHAM.F.SEPT, PHAM.SpSuW.SEPT)

# January
# PHAM all burns 
PHAM.Jan <- as.data.frame(rpois(28, lambda = 5))
PHAM.Jan <- rename(PHAM.Jan, "SEEDS" = "rpois(28, lambda = 5)")
PHAM.Jan$SPECIES <- "PHAM"
PHAM.Jan$DATE <- "JAN"
PHAM.Jan$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
PHAM.Jan$PHENOLOGY <- "F"
PHAM.Jan$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
PHAM.Jan$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
PHAM.Jan$FA <- sum(rbinom(15,1, 0.5))/15

# June
# PHAM all burns 
PHAM.June <- as.data.frame(rpois(28, lambda = 12))
PHAM.June <- rename(PHAM.June, "SEEDS" = "rpois(28, lambda = 12)")
PHAM.June$SPECIES <- "PHAM"
PHAM.June$DATE <- "JUNE"
PHAM.June$TREATMENT <- c("SP","SP","SP","SP","SP","SP","SP",
															"SU","SU","SU","SU","SU","SU","SU",
															"F","F","F","F","F","F","F",
												 "W","W","W","W","W","W","W")
PHAM.June$PHENOLOGY <- "F"
PHAM.June$LOCATION <- c("TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												 "TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF",
												"TT", "TT", "TT", "ENF", "ENF", "ENF", "ENF")
PHAM.June$PLOT <- c("1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										 "1", "2", "3", "13", "14", "15", "16",
										"1", "2", "3", "13", "14", "15", "16")
PHAM.June$FA <- sum(rbinom(15,1, 0.5))/15

PHAM <- rbind(PHAM.June,PHAM.Jan, PHAM.Sept)

### Bring all the species data ####

d <- as.data.frame(rbind(RHGL, RUBUS, ILGL, PHAM, SMRO, CAAM))
```
Then, I create some figures and run a simple analysis, similar to how these are both described in the proposal. The first is a boxplot, grouped by sampling period. Within each peroid, the number of seeds from each phenology group are presented for each treatment. Next, I created a line graph tracking the number of seeds in each treatment across sampling peroids. The colors represent the phenology of the species.

```{r}
ggplot(d,aes(y=SEEDS,x=TREATMENT,color=PHENOLOGY))+
	geom_boxplot()+
	facet_wrap(~DATE)+
	theme_bw()

d_mean <- group_by(d, DATE, TREATMENT,PHENOLOGY) %>% 
					summarise(mean = mean(SEEDS))

ggplot(d_mean,aes(y=mean,x=DATE,group=PHENOLOGY,color=PHENOLOGY))+
	geom_point()+
	geom_line()+
	facet_wrap(~TREATMENT)+
	theme_bw()

library(lme4)
library(car)

d$obs <- 1:length(d$SEEDS)

mod <- glmer(SEEDS ~ FA * TREATMENT * DATE * PHENOLOGY + 
				(1|LOCATION/PLOT) + (1|obs), family="poisson",data = d)

summary(mod)  ## summary for glmmTMB negative binomial
Anova(mod)  ## Anova table for overdispersed poisson

```